If we are talking about dynamic programming most of the times it is an optimization of a solution that use recursion. As we know most of the times use recursion results in an exponential complexity in time so if we find a way to use dynamic programming we can reduce this complexity.\\

\paragraph{What is the main idea of use Dynamic programming?}
The idea is very simple, if we can store the result of the subproblems, we do not need to re-calculate this subproblem and it reduces the complexity from exponential to a polynomial. 

\subsection{Examples}
We can use the idea of calculate a factorial number, we know that a factorial number it is the multiplication of all the numbers from 1 to n, for example

\begin{itemize}
    \item { Calculate 2! = 1 * 2 = 2}
    \item { Calculate 3! = 1 * 2 * 3 = 6}
    \item { Calculate 5! = 1 * 2 * 3 * 4 * 5  = 120}
\end{itemize}

But we need to consider some things about factorial numbers
\begin{enumerate}
    \item { 0! = 1 }
    \item { Factorial numbers exist in range of $[0, \infty)$ }
\end{enumerate}

If we know this we can notice that we can get a formula to simplify this:
\[
    factorial( n ) = 
    \begin{cases*}
        n * factorial(n - 1) & if $n > 1$ \\
        1 & otherwise
    \end{cases*}
\]

Now we can solve this problem using a recursive program, it is very simple because we just need to programm the formula 
\begin{lstlisting}
    #include<bits/stdc++.h>

    using namespace std;
    typedef long long int lli;
    
    lli factorial( int n ){
        if( n > 1 )
            return n * factorial(n);
        return 1;
    }

    int main(){
        int n;
        cin >> n;
        cout << factorial( n ) << endl;
        return 0;
    }
\end{lstlisting}

If we use the last program we can get the factorial of n, but the complexity of this algorithm is $O(n!)$ so it is awful, but using dynamic programming can we get a better complexity? \\

For me is easier to find a solution using dynamic programming using draws, so I go to make the draw of the recursive calls of the example 5!

\begin{figure}[H]
\begin{center}
    \begin{tikzpicture}[scale=0.2]
    \tikzstyle{every node}+=[inner sep=0pt]
    \draw [black] (30.8,-6.3) circle (3);
    \draw (30.8,-6.3) node {$120$};
    \draw [black] (22.1,-17.3) circle (3);
    \draw (22.1,-17.3) node {$5$};
    \draw [black] (40.4,-18) circle (3);
    \draw (40.4,-18) node {$f(4)$};
    \draw [black] (32.6,-27.6) circle (3);
    \draw (32.6,-27.6) node {$4$};
    \draw [black] (48.6,-28.4) circle (3);
    \draw (48.6,-28.4) node {$f(3)$};
    \draw [black] (40.4,-39.4) circle (3);
    \draw (40.4,-39.4) node {$3$};
    \draw [black] (58.1,-40.4) circle (3);
    \draw (58.1,-40.4) node {$f(2)$};
    \draw [black] (65.9,-51.7) circle (3);
    \draw (65.9,-51.7) node {$f(1)$};
    \draw [black] (50.1,-51.1) circle (3);
    \draw (50.1,-51.1) node {$2$};
    \draw [black] (28.94,-8.65) -- (23.96,-14.95);
    \fill [black] (23.96,-14.95) -- (24.85,-14.63) -- (24.07,-14.01);
    \draw [black] (32.7,-8.62) -- (38.5,-15.68);
    \fill [black] (38.5,-15.68) -- (38.38,-14.75) -- (37.6,-15.38);
    \draw [black] (38.51,-20.33) -- (34.49,-25.27);
    \fill [black] (34.49,-25.27) -- (35.38,-24.97) -- (34.61,-24.34);
    \draw [black] (42.26,-20.36) -- (46.74,-26.04);
    \fill [black] (46.74,-26.04) -- (46.64,-25.11) -- (45.85,-25.73);
    \draw [black] (50.46,-30.75) -- (56.24,-38.05);
    \fill [black] (56.24,-38.05) -- (56.13,-37.11) -- (55.35,-37.73);
    \draw [black] (46.81,-30.81) -- (42.19,-36.99);
    \fill [black] (42.19,-36.99) -- (43.07,-36.65) -- (42.27,-36.05);
    \draw [black] (59.8,-42.87) -- (64.2,-49.23);
    \fill [black] (64.2,-49.23) -- (64.15,-48.29) -- (63.33,-48.86);
    \draw [black] (56.3,-42.8) -- (51.9,-48.7);
    \fill [black] (51.9,-48.7) -- (52.78,-48.36) -- (51.97,-47.76);
    \draw [black] (61.058,-40.782) arc (71.94761:-2.71565:8.032);
    \fill [black] (61.06,-40.78) -- (61.66,-41.5) -- (61.97,-40.55);
    \draw (65.78,-42.5) node [right] {$1$};
    \draw [black] (49.475,-48.185) arc (-179.04361:-254.52464:7.711);
    \fill [black] (55.13,-40.63) -- (54.22,-40.36) -- (54.49,-41.32);
    \draw (50.43,-42.04) node [left] {$2$};
    \draw [black] (51.539,-28.946) arc (70.92086:5.81411:10.037);
    \fill [black] (51.54,-28.95) -- (52.13,-29.68) -- (52.46,-28.73);
    \draw (56.69,-30.78) node [right] {$2*1$};
    \draw [black] (39.992,-36.444) arc (-182.37685:-251.02886:8.395);
    \fill [black] (45.65,-28.85) -- (44.73,-28.64) -- (45.06,-29.59);
    \draw (41.07,-30.38) node [left] {$3$};
    \draw [black] (33.712,-6.98) arc (68.73994:9.99869:10.591);
    \fill [black] (33.71,-6.98) -- (34.28,-7.74) -- (34.64,-6.8);
    \draw (38.62,-8.7) node [right] {$4*3*2*1$};
    \draw [black] (21.983,-14.316) arc (-187.14018:-249.5414:9.158);
    \fill [black] (27.87,-6.87) -- (26.94,-6.68) -- (27.29,-7.62);
    \draw (23.32,-8.35) node [left] {$5$};
    \draw [black] (43.329,-18.572) arc (68.89286:7.61598:8.553);
    \fill [black] (43.33,-18.57) -- (43.9,-19.33) -- (44.26,-18.39);
    \draw (47.53,-19.84) node [right] {$3*2*1$};
    \draw [black] (32.353,-24.63) arc (-186.66238:-251.52534:7.525);
    \fill [black] (37.44,-18.37) -- (36.53,-18.15) -- (36.84,-19.09);
    \draw (33.43,-19.33) node [left] {$4$};
    \end{tikzpicture}
\end{center}
\end{figure}

As we can see we the small problem contains information of the base case has information of the next case and this case has information for the next case and so on, so we do not need to call. Maybe if you need to calculate just once a factorial number it is not necessary to store the information about a factorial number but imagine that you are doing a program that needs a lot of factorial numbers, if we use the recursive algorithm without dynamic programming we need to do for each query $O(n!)$ operations, and that is a lot. So we can store this information and make each query a lot of times and if we already calculated a factorial number we just need to return the information and it is $O(1)$

\begin{lstlisting}
    #include <bits/stdc++.h>

    using namespace std;
    typedef long long int lli;

    vector< lli > factorial_number( 1000 + 1, -1 )
    lli factorial( int n ){

        if( factorial_number[ n ] != -1)
            return factorial_number[ n ];

        if( n > 1 )
            return ( factorial_number[ n ] = (n * factorial( n - 1 ) );

        return factorial_number[ n ] = 1;
    }

    int main(){
        int t, n;
        cin >> t;
        while( t-- ){
            cin >> n;
            cout << n << "! = " << factorial( n ) << endl;
        }
        return 0;  
    }
\end{lstlisting}

As you can see we have a little bit of code but we make more efficient get a factorial number, from $O(n!)$ complexity to $O(1)$ in the case of we already calculated the number, but we are using more memory in this case $O(n)$ in other words we are using a container which size is the biggest factorial that we already calculated.\\\\

Other example is calculate Fibonacci numbers, but first of all we need to know what is a factorial number. A factorial number is defined using the next function.

\[
    fibonacci(n) = 
    \begin{cases*}
        0 & if $n \leq 0$ \\    
        n * ( n - 1 ) + ( n - 2 ) & otherwise 
    \end{cases*}    
\]

As the las example we first of all can sole this problem using a recursive algorithm, we just need to program the previous definition of a fibonacci number.

\begin{lstlisting}
    #include<bits/stdc++.h>

    using namespace std;
    typedef long long int lli;

    lli fibonacci( int n ){
        if( n <= 0 )
            return 0;
        return ( n + fibonacci( n - 1 ) + fibonacci( n - 2 ) );
    }

    int main(){
        int n;
        return 0;
    }
\end{lstlisting}

\chapter{Club entrevista}
Generalmente la duración es de 40 - 45 minutos puede extenderse aún más hasta una hora (depende del entrevistador). Microsoft siempre preguntan sobre tu resume, generalmente la pregunta que se da es ''hablame de ti'' , mencionar, desafios, si se habla de desafios hablar sobre los intereses es bastante bueno. Hay que hablar secuencialmente es decir, empecé haciendo tal cosa, empecé en esta área por x, y razón. Mencionar sobre el \textsf{resume} también es importante, siempre hay que ligar lo que se habla con lo que hay ahí. El proceso para la entrevista técnica es, te pongo un problema y si lo solucionas lo complico un poco más, si encuentras la solución se pone uno más complicado.\newline
¿Como solucionar estos problemas?
\begin{itemize}
    \item {Preguntas y más preguntas. Que recibo, que devuelvo, límites, etc. Casos especiales. No hay que dudar en preguntar, el entrevistador es tu amigo, puedes preguntarle, puedes mencionar que no tienes ide sobre como iniciar la solución del problema, suelen dar pistas.}
    \item {Hablar sobre complejidades tanto temporal y espacial. Esto puede ayudar a mejorar la solución que ya se ha dado.}
    \item {Casos de prueba. Generalmente los casos de prueba que dan los entrevistadores, son muy triviales, no nos dan demasiada información sobre el problema.}
    \item {Estructurar una idea: es decir escribir pseudocódigo, hacer un diagrama de flujo, etc. Esto ayuda a saber que estoy haciendo, en que paso voy, etc.}
    \item {Codear: teóricamente es lo más fácil, ya que es solo plasmar la idea. Declarar las variables mencionando que es lo que hacen ayuda bastante.}
    \item {Test: ya se han propuesto test cases, ahora nos toca probar que el código funcione.}
    \item {Feedback: El entrevistador dice \textsf{¿tienes alguna pregunta para mi?} es para ver que tanto interés se tiene por la compañía, por ejemplo si el entrevistador trabaja en el área de Youtube \textsf{¿Porqué el algoritmo de copyright de youtube es tan malo?, ¿Porqué es mejor X compañía que Y?} }
\end{itemize}

Otros consejos 
\begin{itemize}
    \item {Modular el código, hace que luzca bien y hace más sencillo comprender lo que estamos haciendo}
    \item {Funciones que retornen bool que inicien por bool}
    \item {Una función inicia con un verbo}
\end{itemize}

\section{Tipos de entrevistas}

\begin{itemize}
    \item {Juez: tienes 120 minutos para solucionar dos problemas (Google, a veces Facebook)}
    \item {Virtual: Un entrevistador te hace valga la redundancia una entrevista (Facebook, Microsoft, Google)}
    \item {Presencial: tienes un pizarrón blanco y debes solucionar un problema (Microsoft)}
\end{itemize}